Recent advances in smartphone computational photography

### 2020-09-10 annotated-bibliography.tex
Updates from Overleaf

\subsection{Sources I expect to use (and how)}

My primary two sources are \cite{Wronski2019, Liba2019}.

% The following two commands are all you need to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
% annotated_bibliography.bib is the name of the BibTex file containing 
% all the bibliography entries for this example. Note that you *don't* include the .bib ending
% in the \bibliography command.
\bibliography{paper}

>>>>

\subsection{Primary Sources}

My primary two sources are \cite{Wronski2019, Liba2019}.
\begin{itemize}
\item \cite{Wronski2019} describes an algorithm to use natural hand tremor to create higher resolution images from multi-frame bursts. It has the effect of improving image resolution and noise performance.

\item \cite{Liba2019} describes a mobile camera solution leveraging existing burst imaging techniques and improving low-light performance. It builds upon work done in \cite{Hasinoff2016} and uses the burst merging algorithm from \cite{Wronski2019}.
\end{itemize}
Both of these primary sources are long and very detailed. They are written by researchers at Google.

\subsection{Background Sources}
\begin{itemize}
\item \cite{Hasinoff2016} is cited in both of the previous mentioned articles and describes an earlier multi-frame burst merging algorithm. It is used as a point of comparison by both primary sources and will be necessary background information. It is also from Google Research. I think this could end up being more of a primary source.

\end{itemize}
% The following two commands are all you need to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
% annotated_bibliography.bib is the name of the BibTex file containing 
% all the bibliography entries for this example. Note that you *don't* include the .bib ending
% in the \bibliography command.
\bibliography{paper}
